Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-10-13 writing/ehp_methods.tex
Work on writing

This study covered all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}) as of the~2010 \ac{US} Decennial Census. The
study covered all tracked land-falling or near-land Atlantic-basin tropical
cyclones between~1988 and~2015 by considering all 136 storms in \ac{HURDAT2}
\parencite{landsea2013} that came within~250 \si{\kilo\metre} of at least one
eastern \ac{US} county in this period (Figure~\ref{fig:hurrtracks}).

@@

We first measured how close each storm came to each county. We used tracking
data from \ac{HURDAT2}, which records the storm center's position every~6
\si{\hour} (at the synoptic times of 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am
\ac{UTC}), and interpolated this position to~15-\si{\minute} intervals using
natural cubic splines~\parencite{hurricaneexposure}. At each~15-\si{\minute}
interval, we measured the distance between the storm's center and each county's
population mean center~\parencite{bivand2013applied, countycenters}. From these
measurements, we determined how close each storm came to each county.

We also recorded the time the storm came closest to each county. We later used
this time to link observed data on precipitation, flooding, and tornadoes to
the storm.  To allow matching with data recorded in local time (e.g., health
data), we converted these times from \ac{UTC} to local
time~\parencite{countytimezones}.

@@

We based storm rainfall measurements on precipitation data files from the
\ac{NLDAS-2} re-analysis dataset, which is available for the continental
\ac{US}~\parencite{rui2013nldas}. We used data that were previously aggregated
from this re-analysis dataset to the county level for the Centers for Disease
Control and Prevention's \ac{WONDER} database \parencite{cdcwonder} by two of
the coauthors (Al-Hamdan and Crosson) \parencite{alhamdan2014environmental,
cdcwonder}. To create this aggregated data originally, these coauthors took
hourly precipitation measurements in the \ac{NLDAS-1} precipitation files,
which are given at~1/8\si{\degree} grid points across the continential
\ac{US}, and summed them by day for each grid point.  This created a daily
precipitation total for each grid point; these were then averaged for all grid
points within a county's~1990 \ac{US} Census
boundaries~\parencite{alhamdan2014environmental, cdcwonder}. This process
generated daily county-level precipitation estimates for each continental
\ac{US} county for 1988\,--\,2011 \parencite{cdcwonder}.  We matched these
county-level daily measurements by date with storm tracks, using for each
county and storm the date when the storm was closest to the county. Given the
location of storm-affected counties and the typical timing of tropical
cyclones, these precipitation measures primarily represent rainfall, although
occasionally they may represent snowfall or other types of precipitation.

In the open-source data, we provide daily precipitation values for each county
for the period from five days before to three days after each storm's closest
approach to the county.  In the software that we published in association with
this data, we provide the functionality to aggregate these daily values to
create cumulative precipitation estimates for custom windows as needed. For
example, a user could determine precipitation only on the day the storm was
closest to each county, but could also determine the cumulative rainfall for a
more extended period, like from three days before to three days after the
storm's closest approach. For later analysis in this study, we calculated
storm-associated rainfall as the sum of precipitation from two days before the
storm's closest approach to the county to one day after.

To validate these precipitation estimates, we compared them with ground-based
observations in a subset of study counties. We selected nine sample counties
geographically spread across storm-prone regions of the eastern \ac{US} and for
which precipitation data were available from multiple ground-based stations
within the Global Historical Climatology Network throughout the study
period~\parencite{menne2012overview, rnoaa, countyweather}. These sample
counties were: Miami-Dade, FL; Harris County, TX; Mobile County, AL; Orleans
Parish, LA; Fulton County, GA; Charleston County, SC; Wake County, NC;
Baltimore County, MD; and Philadelphia County, PA. We summed daily
station-specific measurements from two days before to one day after each
storm's closest approach and then averaged these cumulative station-based
precipitation totals for each county to create a county-wide estimate of
cumulative storm-related precipitation based on ground-based monitoring. We
measured the rank correlation (Spearman's~$\rho$~\parencite{spearman1904proof})
between storm-specific cumulative precipitation estimates for the two data
sources (\ac{NLDAS} re-analysis data versus ground-based monitoring) within
each sample county.

@@

To create a dataset of county-level sustained winds during historical tropical
cyclones, we modeled maximum sustained wind speeds at each county's population
mean center~\parencite{countycenters}, using a wind speed model based on
results from Willoughby~\parencite{willoughby2006parametric}. For each storm,
we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period, using a double exponential wind speed model with
inputs for the storm's forward speed, direction, and central wind
speed~\parencite{willoughby2006parametric, stormwindmodel}. This model
incorporates the asymmetry in wind speeds around the tropical cyclone center
that results from the storm's forward movement~\parencite{phadke2003modeling,
stormwindmodel}. We then identified the maximum sustained surface wind speed in
each county during each storm.

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we used event listings from the National Oceanic and Atmospheric
Administration (NOAA)'s Storm Event Database~\parencite{stormevents}. While
this database has recorded storm data since~1950, its coverage changed
substantially in~1996 to cover a wider variety of storm
events~\parencite{stormevents}. We therefore only considered these metrics of
hurricane exposure for tropical cyclones in~1996 and later.

@@

For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow~\parencite{countyfloods}) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events in the NOAA Storm Events data versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflows at gages within the county.

@@

In our open-source data, we provide continuous measurements of three exposure
metrics: closest distance of each storm to each county, modeled storm winds,
and storm-related rainfall. However, epidemiologic studies of tropical cyclones
often use a binary exposure classification (``exposed'' versus ``unexposed'')
to assess storm-related health risks [refs], and so we also explored patterns
in storm exposure based on binary clasifications of these exposure metrics.

Two of the exposure metrics (flood- and tornado-based) were inherently binary
in our data, since these metrics were based on whether an event was listed in
the NOAA Storm Events database.  For the other exposure metrics, each county
was classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table~\ref{tab:exposuremetrics}). We
picked reasonable thresholds, but others could be used with the open-source
data and its associated software.

For the rainfall metric, a distance constraint was also necessary, to ensure
that rains unrelated and far from the storm track were not misattributed to a
storm. Through exploratory analysis, we set this distance metric at~500
\si{\kilo\metre} (i.e., for a county to be classified as exposed based on
rainfall, the cumulative rainfall in the county had to be over the
75~\si{\milli\metre} threshold and the storm must have passed within~500
\si{\kilo\metre} of the county; Table~\ref{tab:exposuremetrics}). This distance
constraint was typically large enough to capture storm-related rain.  However,
data users should note that in rare cases---for example, exceptionally large
storms (e.g., Hurricane Ike in 2008) or storms for which storm tracking was
stopped at extratropical transition (e.g., Tropical Storm Lee in 2011)---some
storm-related rains may be missed because of this distance constraint
(Figure~S1). This distance constraint can be customized using the software
published in association with the open-source
data~\parencite{hurricaneexposure}.

We characterized patterns in county-level exposure in the eastern \ac{US} for
each of the measured tropical cyclone hazards (extreme precipitation, maximum
sustained winds, flooding, and tornadoes).  Depending on available exposure
data, this assessment included some or all of the period from~1988 to~2015
(Table 1). For each binary metric of exposure to a tropical cyclone hazard, we
first summed the total number of county-level exposures over available years
for each exposure metric and mapped patterns in these exposures. We next
investigated agreement between storm exposure classifications based on these
different single-hazard exposures, as well as between each of these and a
distance-based proxy assessment of tropical cyclone exposure
(Table~\ref{tab:exposuremetrics}). We calculated the within-storm Jaccard
index~\parencite{jaccard1901distribution, jaccard1908nouvelles} between each
pair of exposure metrics. The Jaccard index~($J_s$) measures similarity between
two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We measured these values for all study storms that affected a
large number of eastern \ac{US} counties (those storms with 250 or more of the
study counties classified as exposed by at least one of the exposure metrics)
during the years when all exposure data were available (1996\,--\,2011).

@@

We collected data on the number of electricity-dependent Medicare beneficiaries
in each study county from the \ac{US} Department of Health \& Human Service's
emPower Map~2.0~\parencite{empower}. This subpopulation was selected since it
may be particularly susceptible to health impacts from tropical cyclone
exposure, especially through the pathway of storm-associated power outages and
evacuations. We calculated the physical exposure of the electricity-dependent
Medicare population in each county, based on tropical cyclone assessments using
each exposure metric (Table~\ref{tab:exposuremetrics}), following
\citeauthor*{peduzzi2009assessing}~(\citeyear{peduzzi2009assessing}):

>>>>

We aggregated data for all counties in the eastern half of the \ac{US}
(Figure~\ref{fig:hurrtracks}) as of the~2010 \ac{US} Decennial Census and for
all tracked land-falling or near-land Atlantic-basin tropical cyclones
between~1988 and~2015---all 136 storms in \ac{HURDAT2} \parencite{landsea2013}
that came within~250 \si{\kilo\metre} of at least one eastern \ac{US} county in
this period (Figure~\ref{fig:hurrtracks}).

@@

We first measured how close each storm came to each county. We used tracking
data from \ac{HURDAT2}, which records the storm center's position every~6
\si{\hour} (at the synoptic times of 6:00~am, 12:00~pm, 6:00~pm, and 12:00~am
\ac{UTC}), and interpolated this position to~15-\si{\minute} intervals using
natural cubic splines~\parencite{hurricaneexposure}. At each~15-\si{\minute}
interval, we measured the distance between the storm's center and each county's
population mean center~\parencite{bivand2013applied, countycenters}. We took
the minimum for each county as a measure of how close the storm came to the
county.  We also recorded the time the storm came closest to each county, which
we later used to link observed data on precipitation, flooding, and tornadoes
to the storm.  To allow matching with data recorded in local time (e.g., health
data), we converted these times from \ac{UTC} to local
time~\parencite{countytimezones}.

@@

We based storm rainfall measurements on precipitation data files from the
\ac{NLDAS-2} re-analysis dataset, which is available for the continental
\ac{US}~\parencite{rui2013nldas}. We used data that were previously aggregated
from this re-analysis dataset to the county level by two of the coauthors
(Al-Hamdan and Crosson) for the Centers for Disease Control and Prevention's
\ac{WONDER} database \parencite{cdcwonder, alhamdan2014environmental}. To
create this aggregated data originally, these coauthors took hourly
precipitation measurements in the \ac{NLDAS-2} precipitation files, which are
given at~1/8\si{\degree} grid points across the continential \ac{US}, and
summed them by day for each grid point.  This created a daily precipitation
total for each grid point; these were then averaged for all grid points within
a county's~1990 \ac{US} Census boundaries~\parencite{alhamdan2014environmental,
cdcwonder}. This process generated daily county-level precipitation estimates
for each continental \ac{US} county for 1988\,--\,2011 \parencite{cdcwonder}.
We matched these county-level daily measurements by date with storm tracks,
using for each county and storm the date when the storm was closest to the
county. Given the location of storm-affected counties and the typical timing of
tropical cyclones, these precipitation measures primarily represent rainfall,
although occasionally they may represent snowfall or other types of
precipitation.

In the open-source data~\parencite{hurricaneexposuredata}, we provide daily
precipitation values for each county for the period from five days before to
three days after each storm's closest approach to the county.  In the software
that we published in association with this data~\parencite{hurricaneexposure},
we provide functionality to aggregate these daily values to create cumulative
precipitation estimates for custom windows around the date of the storm's
closest approach to the county. For example, a user could determine
precipitation only on the day the storm was closest to each county, but could
also determine the cumulative rainfall for a more extended period, like from
three days before to three days after the storm's closest approach. For the
analysis of binary exposure classifications in this study, we calculated
storm-associated rainfall as the sum of precipitation from two days before the
storm's closest approach to the county to one day after.

To validate these precipitation estimates, we compared them with ground-based
observations in a subset of study counties. We selected nine sample counties
geographically spread across storm-prone regions of the eastern \ac{US} and for
which precipitation data were available from multiple ground-based stations
within the Global Historical Climatology Network throughout the study
period~\parencite{menne2012overview, rnoaa, countyweather}. These sample
counties were: Miami-Dade, FL; Harris County, TX; Mobile County, AL; Orleans
Parish, LA; Fulton County, GA; Charleston County, SC; Wake County, NC;
Baltimore County, MD; and Philadelphia County, PA. We summed daily
station-specific measurements from two days before to one day after each
storm's closest approach and then averaged these cumulative station-based
precipitation totals for each county to create a county-wide estimate of
cumulative storm-related precipitation based on ground-based monitoring. We
measured the rank correlation (Spearman's~$\rho$~\parencite{spearman1904proof})
between storm-specific cumulative precipitation estimates for the two data
sources (\ac{NLDAS-2} re-analysis data versus ground-based monitoring) within
each sample county.

@@

To create a dataset of county-level maximum sustained winds during historical
tropical cyclones, we modeled maximum sustained wind speeds at each county's
population mean center~\parencite{countycenters} using a wind speed model based
on results from Willoughby~\parencite{willoughby2006parametric}. For each
storm, we modeled the maximum ground-level sustained wind speed that the storm
generated at each county center for each~15-\si{\minute} increment throughout
the storm tracking period, using a double exponential wind speed model with
inputs for the storm's forward speed, direction, and maximum wind
speed~\parencite{willoughby2006parametric, stormwindmodel}. This model
incorporates the asymmetry in wind speeds around the tropical cyclone center
that results from the storm's forward movement~\parencite{phadke2003modeling,
stormwindmodel}. We then identified the maximum sustained surface wind speed in
each county during each storm.

@@

To identify flood- and tornado-based tropical cyclone exposures in \ac{US}
counties, we used event listings from the National Oceanic and Atmospheric
Administration (NOAA)'s Storm Event Database~\parencite{stormevents}. While
this database has recorded storm data since~1950, its coverage changed
substantially in~1996 to cover a more types of storm
events~\parencite{stormevents}. We therefore only considered these metrics of
hurricane exposure for tropical cyclones in~1996 and later.

@@

For each storm and county, we summed streamflow measurements across all county
gages to generate daily totals for the five-day window around the storm's
closest approach. We took the maximum of these daily streamflow totals as a
measure of the county's maximum daily streamflow during that storm. We also
calculated the percent of streamflow gages in the county with a daily
streamflow that exceeded a threshold of flooding (the streamgage's median value
for annual peak flow~\parencite{countyfloods}) on any day during the five-day
window. We investigated how these measurements varied between storms with
associated flood events listed in the NOAA Storm Events data versus storms without an
event listing for the county, to explore if storms with flood event listings
tended to be associated with higher streamflow at gages within the county.

@@

In our open-source data, we provide continuous measurements of three exposure
metrics: closest distance of each storm to each county, maximum sustained winds
at the county center, and cumulative rainfall. However, epidemiologic studies
of tropical cyclones often use a binary exposure classification (``exposed''
versus ``unexposed'') to assess storm-related health risks, and so we
explored patterns in storm exposure based on binary clasifications of
these exposure metrics.

Two of the exposure metrics (flood- and tornado-based) were inherently binary
in our data, since these metrics were based on whether an event was listed in
the NOAA Storm Events database.  For other exposure metrics, each county
was classified as exposed to a tropical cyclone based on whether the exposure
metric exceeded a certain threshold (Table~\ref{tab:exposuremetrics}). We
picked reasonable thresholds, but others could be used with the open-source
data and its associated software.

For the rainfall metric, a distance constraint was also necessary, to ensure
that rainfall unrelated and far from the storm track were not misattributed to a
storm. Through exploratory analysis, we set this distance metric at~500
\si{\kilo\metre} (i.e., for a county to be classified as exposed based on
rainfall, the cumulative rainfall in the county had to be over the
75~\si{\milli\metre} threshold and the storm must have passed within~500
\si{\kilo\metre} of the county; Table~\ref{tab:exposuremetrics}). This distance
constraint was typically large enough to capture storm-related rain.  However,
data users should note that in rare cases---for example, exceptionally large
storms (e.g., Hurricane Ike in 2008) or storms for which storm tracking was
stopped at extratropical transition (e.g., Tropical Storm Lee in 2011)---some
storm-related rain exposures may be missed because of this distance constraint
(Figure~S1). This distance constraint can be customized using the software
published in association with the open-source
data~\parencite{hurricaneexposure}.

We characterized patterns in county-level exposure in the eastern \ac{US} for
exposure assessment based on each of the measured tropical cyclone hazards
(cumulative precipitation, maximum sustained winds, flooding, and tornadoes).
Depending on available exposure data, this assessment included some or all of
the period from~1988 to~2015 (Table 1). For each binary metric of exposure to a
tropical cyclone hazard, we first summed the total number of county-level
exposures over available years and mapped patterns in
these exposures. We next investigated agreement between storm exposure
classifications based on these different single-hazard exposures, as well as
between each of these and a distance-based proxy assessment of tropical cyclone
exposure (Table~\ref{tab:exposuremetrics}). We calculated the within-storm
Jaccard index~\parencite{jaccard1901distribution, jaccard1908nouvelles} between
each pair of exposure metrics. The Jaccard index~($J_s$) measures similarity
between two metrics ($X_{1,s}$ and~$X_{2,s}$) for tropical cyclone~$s$ as the
proportion of counties in which both of the metrics classify the county as
exposed out of all counties classified as exposed by at least one of the
metrics:

@@

\noindent This metric can range from~0, in the case of no overlap between the
counties classified as exposed based on the two metrics, to~1, in the case that
the two metrics classify exactly the same set of counties as exposed to the
tropical cyclone. We measured these values for all study storms that affected a
large number of eastern \ac{US} counties (those storms with 100 or more
counties were classified as exposed by at least one of the exposure metrics)
during the years when all exposure data were available (1996\,--\,2011).

@@

We collected data on the number of electricity-dependent Medicare beneficiaries
in each study county from the \ac{US} Department of Health \& Human Service's
emPower Map~2.0~\parencite{empower}. This subpopulation was selected because it
may be particularly susceptible to health impacts from tropical cyclone
exposure, especially through the pathway of storm-associated power outages and
evacuations. We calculated the physical exposure of the electricity-dependent
Medicare population in each county, based on tropical cyclone assessments using
each exposure metric (Table~\ref{tab:exposuremetrics}), following
\citeauthor*{peduzzi2009assessing}~(\citeyear{peduzzi2009assessing}):

### 2019-10-13 writing/ehp_results.tex
Work on writing

We created and published this tropical cyclone exposure data as an open-source
dataset, so they can be used by epidemiological
researchers~\parencite{hurricaneexposuredata}. These data include continuous
county-level measurements for the closest distance of each storm, cumulative
rainfall, and maximum sustained surface wind speed. These continuous metrics
can be used for classifying counties as exposed or unexposed, using thresholds
selected by the user, or can be used as continuous metrics. The dataset also
include binary data on flood and tornado events associated with each storm in
each county. To accompany these data, we published software tools to explore
and map the data and to integrate it with human health
datasets~\parencite{hurricaneexposure}.

@@

For flood data, we compared flood status, based on event listings in the NOAA
Storm Events database and included in the open-source data, to streamflow
measurements at \ac{US} Geological Survey gages within nine sample counties
(Figure~\ref{fig:floodcomparison}). Across the sampled counties, streamgage
data generally indicated higher discharge during periods identified as flood
events based on the NOAA Storm Events database, particularly in counties with
more reporting streamgages (e.g., Harris County, TX, with~10 reporting stream
gages; Figure~\ref{fig:floodcomparison}). There were some cases, however, where
the two flooding data sources were somewhat inconsistent.  For example, there
were one or two tropical cyclones in several of the counties (Mobile County,
AL, Escambia County, FL, and Montgomery County, PA) with associated flood event
listings but for which the total discharge across county streamflow gages was
below the 25\textsuperscript{th} percentile of measurements during storms
without a flood event listing in that county. For storms without a flood
listing for the county, in most cases the total streamflow discharge in
the county was lower than during storms for which there were flood
event listings. Further, in all but one of these cases, all streamgage flows
were below the flooding threshold. The exception was one storm in Fulton
County, GA (Hurricane Ida in 2009).

@@

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. Across the four storm hazards considered,
there was wide variation in the average number of county exposures per year
(Table~\ref{tab:exposuresummaries}). For the tropical cyclone tornado exposure,
there were on average about 50 county exposures per year within our study. For
tropical cyclone flood and wind exposures, county exposures were much more
frequent ($>$200 / yr on average), and even more when assessing tropical
cyclone rain exposure ($>$400 / yr on average).

We also measured the average number of counties exposed per storm to each
hazard (limiting this analysis to the tropical cyclones that exposed at least
one county to that hazard; Table~\ref{tab:exposuresummaries}).  Tropical
cyclones typically exposed only a few counties, if any, to tornadoes (median
counties exposed per storm:~7), more counties to flooding and high winds
(median:~26 and~34, respectively), and even more counties to extreme rain
(median:~68).  For every hazard except tropical cyclone tornadoes, we
identified at least one tropical cyclone that exposed over~300 counties.
However, the largest-extent tropical cyclone varied across hazards: Frances
in~2004 exposed the most counties based on rain, Ike in~2008 based on wind, and
Ivan in 2004 based on flooding and tornadoes
(Table~\ref{tab:exposuresummaries}).

When we calculated and mapped the average number of exposures per decade in
each county for single-hazard exposures (Figure~\ref{fig:averageexposure}),
strong geographical patterns were clear. Tropical cyclone wind exposure had a
strong coastal pattern, with almost all exposures in counties within about~200
\si{\kilo\metre} (124~mi) of the coastline. While tropical cyclone rain
exposure was also more frequent in coastal areas compared to inland areas,
there were also inland exposures in counties not often  that were not
identified as exposed by the wind-based metric. Rain and, to some extent, flood
exposures were characterized by a pattern defined by the Appalachian Mountains,
with many fewer exposures west of the mountain range than to the east. Almost
all tornado-based exposures were in coastal states, with most in Florida,
Alabama, South Carolina, and North Carolina and almost none north of Maryland.
Flood-based exposures were highest in North Carolina and along the South
Carolina coast, as well as further north in New Jersey, southeastern
Pennsylvania, and southeastern New York. Notably, some areas of the \ac{US}
that experienced regular exposures to tropical cyclone-related excessive
rainfall and floods were not identified as areas of regular risk based on the
more commonly used tropical cyclone exposure assessment metrics of wind or
distance (Figure~\ref{fig:averageexposure}).  Patterns were similar when
analysis was restricted to years with exposure data for all four hazards
available (1996\,--\,2011; Figure~S3).

@@

Next, we measured the agreement between exposure classifications for each pair
of metrics. We found that these exposure classifications typically did not
strongly agree between pairs of metrics. The set of counties
identified as ``exposed'' based on one metric often overlap little with
the set identified as ``exposed'' by another metric.

Figure~\ref{fig:ivanexposure} shows shows an example: Hurricane Ivan in 2004.
For the distance-based metric, the counties assessed as exposed followed the
tropical cyclone's track, including counties well inland. For the wind metric,
only counties near two of the tropical cyclone's landfalls were assessed as
exposed. For rain- and flood-based metrics, however, exposure extended to the
left of the track, including counties as far north as New York and Connecticut,
while for the tornado metric, exposed counties tended to be to the right of the
track and included several counties in central North Carolina, South Carolina,
and Georgia that were not identified as exposed to Ivan based on any other
metric. Figure~S4 provides similar maps for four other example tropical
cyclones (selected because they exposed many \ac{US}  counties based on at
least one metric), and Figure~S5 provides four examples of tropical cyclones in
which the disagreement in exposure assessment between rain- and wind-based
metrics was particularly notable.

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (the period for which data for all five metrics were
available) for which~250 or more counties were exposed based on at least one
metric (Figure~\ref{fig:jaccard}). In this figure, each row provides results
for one tropical cyclone, and each box in that row shows the measured Jaccard
coefficient a pair of exposure metrics. For most tropical cyclones,
distance-based county-level exposure assessment was, at best, in moderate
agreement with exposure assessments based on the four hazard-based metrics. For
almost all tropical cyclones, Jaccard index values between distance and any of
the four hazard-based metrics were~$\le0.6$ (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
fewer were assessed the same under both metrics in the pair). For many tropical
cyclones, the Jaccard index values were~$\le0.2$, indicating poor agreement.
Among the four hazard-based metrics, the tornado-based metric had
universally poor agreement with other metrics in county-level classification
across the tropical cyclones considered.  For other pairs of metrics, there was
also generally disagreement in which counties were determined to be exposed,
with Jaccard index values~$<0.4$ for most metric pairs in most tropical
cyclones.

There were, however, exceptions\,---\,tropical cyclones in which exposure
assessment agreed well across several of the metrics considered.  For Floyd
in~1999 (Figure~S4) and Irene in~2011, for example, county-level classification
agreed moderately to well (Jaccard index of~$\sim 0.5\mbox{\,--\,}0.8$) for all
pairs of exposure metrics except those including the tornado-based metric. For
another set of tropical cyclones (e.g., Lee in~2011 [Figure~S3], Ernesto
in~2006, and Bertha in~1996), there was moderate to good agreement for all
pairwise combinations of distance, rain, and wind, but poor agreement for all
other combinations of metrics.  However, these two sets of tropical cyclones
represented the minority of tropical cyclones considered; for most tropical
cyclones, there was low overlap in the counties determined to be exposed to the
tropical cyclones between most pairings of metrics.

@@

We conducted a case study comparing estimates of physical exposure to
tropical cyclones that were measured using each exposure metric.
Figure~\ref{fig:topelecdependexposure} shows the study counties with the
highest expected physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries based on each metric. A few
counties (Miami-Dade County, FL; Harris County, TX) were ranked in the top
three under almost all exposure metrics
(Figure~\ref{fig:topelecdependexposure}). However, there were key differences
across exposure metrics. For example, most of the top counties based on wind-
and tornado-based metrics were in Florida, while over half of the top counties
based on the flood-based metric were in Mid-Atlantic states (PA, NY).

>>>>

We created and published this tropical cyclone exposure data as open-source
data, so they can be used by epidemiological
researchers~\parencite{hurricaneexposuredata}. These data include continuous
county-level measurements for the closest distance of each storm, cumulative
rainfall, and maximum sustained surface wind speed. These continuous metrics
can be used for classifying counties as exposed or unexposed, using thresholds
selected by the user, or can be used as continuous metrics. The dataset also
include binary data on flood and tornado events associated with each storm in
each county. To accompany these data, we published software tools to explore
and map the data and to integrate it with human health
datasets~\parencite{hurricaneexposure}.

@@

For flood data, we compared flood status, based on event listings in the NOAA
Storm Events database and included in the open-source data, to streamflow
measurements at \ac{US} Geological Survey gages within nine sample counties
(Figure~\ref{fig:floodcomparison}). Across the sampled counties, streamgage
data generally indicated higher discharge during periods identified as flood
events based on the NOAA Storm Events database, particularly in counties with
more reporting streamgages (e.g., Harris County, TX, with~10 reporting stream
gages; Figure~\ref{fig:floodcomparison}). There were some cases, however, where
the two flooding data sources were somewhat inconsistent.  For example, there
were one or two tropical cyclones in several of the counties (Mobile County,
AL, Escambia County, FL, and Montgomery County, PA) with associated flood event
listings but for which the total discharge across county streamflow gages was
relatively low. For storms without a flood listing for the county, in most
cases the total streamflow discharge in the county was relatively low, and, in
all but one of these cases all streamgage flows were below the flooding
threshold. The exception was for one storm in Fulton County, GA (Hurricane Ida
in 2009).

@@

We used this storm exposure data to classify counties as exposed or unexposed
to four different hazards for each tropical cyclone and then explored patterns
over years with available data. Across the four storm hazards considered, there
was wide variation in the average number of county exposures per year
(Table~\ref{tab:exposuresummaries}). For the tropical cyclone tornado exposure,
there were on average about 50 county exposures per year within our study.
County exposures were more frequent for tropical cyclone wind exposures ($>$140
/ yr on average), even more frequent for tropical cyclone flood exposures
($>$200 / yr on average), and most frequent for tropical cyclone rain exposure
($>$400 / yr on average).

We also measured the average number of counties exposed per storm to each
hazard (limiting this analysis to tropical cyclones that exposed at least one
county to that hazard; Table~\ref{tab:exposuresummaries}).  If a tropical
cyclone exposed any counties to tornadoes, it was typically only a few (median
counties exposed per storm:~7). When a storm exposed any counties to other
tropical cyclone exposures, the swath of exposed counties tended to be much
larger: a median of~25 counties exposed for high winds per storm,~26 for
flooding, and~68 for extreme rainfall.  For every hazard except tropical
cyclone tornadoes, we identified at least one tropical cyclone that exposed
over~250 counties (Table~\ref{tab:exposuresummaries}).  However, the
largest-extent tropical cyclone varied across hazards: Frances in~2004 exposed
the most counties based on rain, Ike in~2008 based on wind, and Ivan in 2004
based on flooding and tornadoes (Table~\ref{tab:exposuresummaries}).

When we calculated and mapped the average number of exposures per decade in
each county for single-hazard exposures (Figure~\ref{fig:averageexposure}),
strong geographical patterns were clear. Tropical cyclone wind exposure had a
strong coastal pattern, with almost all exposures in counties within about~200
\si{\kilo\metre} (124~mi) of the coastline. While tropical cyclone rain
exposure was also more frequent in coastal areas compared to inland areas,
there were also inland exposures in counties that were never to extreme storm
winds. Rain and, to some extent, flood exposures were characterized by a
pattern defined by the Appalachian Mountains, with fewer exposures west of the
mountain range than to the east. Almost all tornado-based exposures were in
coastal states, with many in Florida, and almost none north of Maryland.
Flood-based exposures were frequently in the Mid-Atlantic region, with a
pattern that skewed north compared with other exposures.  Patterns were similar
when analysis was restricted to years with exposure data for all four hazards
available (1996\,--\,2011; Figure~S3).

@@

Next, we measured the agreement between exposure classifications for each pair
of hazards, as well as between each hazard and exposure assessment based on
distance from the storm's track as a proxy for exposure to storm hazards. We
found that these exposure classifications typically did not strongly agree
between pairs of metrics. The set of counties identified as ``exposed'' based
on one metric often overlap little with the set identified as ``exposed'' by
another metric, as storms frequently brought different hazards to different 
locations.

Figure~\ref{fig:ivanexposure} shows shows an example: Hurricane Ivan in 2004.
For the distance-based metric, the counties assessed as exposed follow the
tropical cyclone's track. For the wind-based metric,
only counties near the tropical cyclone's first landfall were assessed as
exposed. For rain- and flood-based metrics, however, exposure extended to the
left of the track, including counties as far north as New York and Connecticut,
while for the tornado metric, exposed counties tended to be to the right of the
track and included several counties in central North Carolina, South Carolina,
and Georgia that were not identified as exposed to Ivan based on any other
metric. Figure~S4 provides similar maps for four other example tropical
cyclones (selected because they exposed many \ac{US}  counties based on at
least one metric).

We drew similar conclusions when we investigated all~46 tropical cyclones
between~1996 and~2011 (the period for which data for all five metrics were
available) for which~100 or more counties were exposed based on at least one
metric (Figure~\ref{fig:jaccard}). In this figure, each row provides results
for one tropical cyclone, and each box in that row shows the measured Jaccard
coefficient for a pair of metrics. For most tropical cyclones,
distance-based county-level exposure assessment was, at best, in moderate
agreement with exposure assessments based on the four hazard-based metrics. For
almost all tropical cyclones, Jaccard index values between distance and any of
the four hazard-based metrics were~$\le0.6$ (i.e., out of the counties assessed
as exposed by at least one of the two metrics in the pair,~60\si{\percent} or
fewer were assessed the same under both metrics in the pair). For many tropical
cyclones, the Jaccard index values were~$\le0.4$, indicating poor agreement.
Among the four hazard-based metrics, the tornado-based metric had
universally poor agreement with other metrics in county-level classification
across the tropical cyclones considered.

There were, however, exceptions\,---\,tropical cyclones in which exposure
assessment agreed well across several of the metrics considered.  For Floyd
in~1999 (Figure~S4) and Irene in~2011, for example, county-level classification
agreed moderately to well for all pairs of exposure metrics except those
including the tornado-based metric (Figure~\ref{fig:jaccard}). For another set
of tropical cyclones (e.g., Ernesto in~2006, and Bertha in~1996, Isabel
in~2003), there was moderate to good agreement for all pairwise combinations of
distance, rain, and wind, but poor agreement for all other combinations of
metrics, while for another set of storms (e.g., Matthew in~2004 and Katrina
in~2005), there was moderate to good agreement between distance and rain.
However, these sets of tropical cyclones represented the minority of tropical
cyclones considered; for most tropical cyclones, there was low overlap in the
counties determined to be exposed to the tropical cyclones between most
pairings of metrics.

@@

We conducted a case study comparing estimates of physical exposure to
tropical cyclones that were measured using each exposure metric.
Figure~\ref{fig:topelecdependexposure} shows the study counties with the
highest expected rates of physical exposure to tropical cyclones among
electricity-dependent Medicare beneficiaries based on each metric. A few
counties (Miami-Dade County, FL; Harris County, TX) were ranked in the top
three under almost all exposure metrics
(Figure~\ref{fig:topelecdependexposure}). However, there were key differences
across exposure metrics. For example, most of the top counties based on wind-
and tornado-based metrics were in Florida, while over half of the top counties
based on the flood-based metric were in Mid-Atlantic states (PA, NY).
